XXXXX

### 2014-12-20 paper/RDF validation requirements/RDF validation requirements.tex
classification

>>>>

We evaluated to which extend the most promising five DSCLs fulfill each requirement.
Tilde means that this constraint may be fulfilled by that particular constraint language - either by limitations, workarounds, or extensions.
We also evaluated if a specific constraint is fulfilled by OWL 2 QL or if the more expressive OWL 2 DL is needed. 
Inferencing may be performed prior to validating constraints. This is marked with an asterisk.
